
In the first 2 steps, we selected the best distribution and degree of freedom via BIC. Now we are gonna use this script to perform model evaluation, sensitivity analyses, and visualization of normative trajectories.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(ggplot2)
library(tidyverse)
library(mgcv)
library(readxl)
library(parallel)
library(gamlss)
library(scales)
library(stringr)
# input directory
wd <- getwd()
if (str_detect(wd, "cuizaixu_lab")){
  datapath <- '/ibmgpfs/cuizaixu_lab/tanlirou1/Yunfu/YF_EF_psy/data'
  interfileFolder <- "/ibmgpfs/cuizaixu_lab/tanlirou1/Yunfu/YF_EF_psy/interfileFolder"
  functionFolder <- "/ibmgpfs/cuizaixu_lab/tanlirou1/Yunfu/YF_EF_psy/Rcode/functions"
  resultFolder <- "/ibmgpfs/cuizaixu_lab/tanlirou1/Yunfu/YF_EF_psy/results"
  FigureFolder <- "/ibmgpfs/cuizaixu_lab/tanlirou1/Yunfu/YF_EF_psy/FigureFolder"
}else{
  datapath <- 'V:/yunfu_data/EF_results'
  demopath <- 'V:/rawdata/rawdata_results0616'
  FigureFolder <- 'Z:/DMRI_network_development/EF_development/Crsen_survey_GD_YunFu/Figures'
  interfileFolder <- "Z:/DMRI_network_development/EF_development/Crsen_survey_GD_YunFu/interfileFolder"
  functionFolder <- "Z:/DMRI_network_development/EF_development/Crsen_survey_GD_YunFu/Rcode_EFnorms/functions"
  resultFolder <- "Z:/DMRI_network_development/EF_development/Crsen_survey_GD_YunFu/results"
  
}

GNG_data <- read_xlsx(paste0(datapath, "/Q_GNG.xlsx"))
back1_data <- read_xlsx(paste0(datapath, "/Q_1back.xlsx"))
back2_data <- read_xlsx(paste0(datapath, "/Q_2back.xlsx"))
```

## Step3. Model evaluation
### 1. model diagnosis
The normalized quantile residuals of our normative model were also checked to evaluate the goodness of fit by utilizing two diagnostic methods.
1) Inspect four plots related to residuals. The residuals against the fitted values of mu and the index were evenly distributed around the horizontal line at 0. Moreover, the kernel density estimation of the residuals displayedan approximate normal distribution, and the normal quantile-quantile (Q-Q) plots exhibitedan approximately linear trend with an intercept of 0 and a slope of 1.
2) Adopt the detrended transformed Owen's plots of the fitted normalized quantile residuals to evaluate the performance of the models. The function uses Owen's method to construct a nonparametric confidence interval for the true distribution.The zero horizontal line was within the confidence intervals, suggesting that the residuals followed a normal distribution. Taken together, these results showed that our model fits the sample data appropriately.

```{r S3_1_mod_diagnosis}
# 1. GNG d_prime
# visualize the distribution of dependent variable
plot(density(GNG_data$d_prime), main = "Density Plot of Go/No-go d_prime", xlab = "Value", col = "blue")
# load models
performance_GNGd_prime_distribution <- read.csv(paste0(resultFolder, "/performance_GNGd_prime_distribution.csv"))
modelsum_GNGd_prime_distribution <- readRDS(paste0(resultFolder, "/modelsum_GNGd_prime_distribution.rds"))
performance_GNGd_prime_bsdf <- read.csv(paste0(resultFolder, "/performance_GNGd_prime_bsdf.csv"))
modelsum_GNGd_prime_bsdf <- readRDS(paste0(resultFolder, "/modelsum_GNGd_prime_bsdf.rds"))
# performance bic
performance_GNGd_prime_distribution_adj <- performance_GNGd_prime_distribution %>% drop_na()
performance_GNGd_prime_distribution_adj <- performance_GNGd_prime_distribution_adj %>% 
  filter(converged == TRUE) %>%
  mutate(BIC_adjusted = BIC - max(BIC)) %>% 
  arrange(BIC_adjusted) %>% 
  slice(1:10)
performance_GNGd_prime_distribution_adj <- performance_GNGd_prime_distribution_adj[order(performance_GNGd_prime_distribution_adj$BIC, decreasing = F),]
performance_GNGd_prime_distribution_adj$distribution <- factor(performance_GNGd_prime_distribution_adj$distribution, levels=performance_GNGd_prime_distribution_adj$distribution)
ggplot(data = performance_GNGd_prime_distribution_adj, aes(x = distribution, y = BIC_adjusted)) +
  geom_bar(stat = "identity", fill = "#A4C5DF", color = "black", size = 0.5, width = 0.7) +
  labs(title = "Go/No-go", 
       x = "Distribution", y = expression(BIC~(x~10^2))) +  # Add a multiplier annotation to the y-axis
  theme_minimal() +
  theme(
    plot.title = element_text(size = 8.5, hjust = 0.5),
    axis.text.x = element_text(size = 8.5, color = "black", angle = 45, hjust = 1),
    axis.text.y = element_text(size = 8.5, color = "black"),
    axis.title= element_text(size = 8.5, color = "black"),
    axis.line = element_blank(), # Remove default axis lines
    axis.ticks = element_line(color = "black", size = 0.5), # Customize tick marks
    axis.ticks.length = unit(-0.2, "cm"), # Move tick marks inside the axis
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank(), # Remove minor grid lines
    panel.border = element_rect(color = "black", fill = NA, size = 1) # Add a border around x and y axes
  ) +
  scale_x_discrete(
    expand = expansion(mult = 0.1) # Add padding at both ends of the x-axis
  ) +
  coord_cartesian(ylim = c(min(performance_GNGd_prime_distribution_adj$BIC_adjusted), max(performance_GNGd_prime_distribution_adj$BIC_adjusted))) + # Enforce the y-axis range
  scale_y_continuous(
    breaks = seq(-800, -200, by = 200), # Set y-axis tick intervals
    labels = function(x) x / 100, # Adjust y-axis tick labels to a simpler scientific format
    expand = c(0, 0) # Remove default padding
  )

ggsave(paste0(FigureFolder, "/Gonogo/distribution_BIC_GNGd_prime.pdf"), width=9, height=7, units = "cm")
ggsave(paste0(FigureFolder, "/Gonogo/distribution_BIC_GNGd_prime.tiff"), width=9, height=7, units = "cm")

# Remove rows with missing values and order by BIC in ascending order
performance_GNGd_prime_bsdf_adj<- performance_GNGd_prime_bsdf %>% 
  drop_na() %>%
  arrange(BIC)

# Select the 10 smallest BIC values
performance_GNGd_prime_bsdf_adj<- performance_GNGd_prime_bsdf_adj[1:10, ]

# Create a label for degrees of freedom
performance_GNGd_prime_bsdf_adj$bsdf <- paste0(
  "mu", performance_GNGd_prime_bsdf_adj$mu.df, 
  "_sigma", performance_GNGd_prime_bsdf_adj$sigma.df, 
  "_degree", performance_GNGd_prime_bsdf_adj$degree
)

# Convert bsdf to a factor with levels ordered by BIC
performance_GNGd_prime_bsdf_adj$bsdf <- factor(performance_GNGd_prime_bsdf_adj$bsdf, levels = performance_GNGd_prime_bsdf_adj$bsdf)

# Adjust BIC values by subtracting the maximum value
performance_GNGd_prime_bsdf_adj$BIC_adjusted <- performance_GNGd_prime_bsdf_adj$BIC - max(performance_GNGd_prime_bsdf_adj$BIC)

# Plot
ggplot(data = performance_GNGd_prime_bsdf_adj) +
  geom_bar(aes(x = bsdf, y = BIC_adjusted), stat = "identity", 
           position = "dodge", fill = "#A4C5DF", color = "black", size = 0.5, width = 0.7) +
  labs(title = "Go/No-go", 
       x = "Degree of freedom", y = expression(BIC~(x~10))) +  # Add axis labels with BIC multiplier
  theme_minimal() +
  theme(
    plot.title = element_text(size = 8.5, hjust = 0.5),
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8.5, color = "black"), # Adjust x-axis text
    axis.text.y = element_text(size = 8.5, color = "black"), # Adjust y-axis text
    axis.title.x = element_text(size = 8.5, color = "black"), # Adjust x-axis title
    axis.title.y = element_text(size = 8.5, color = "black"), # Adjust y-axis title
    axis.line = element_blank(), # Remove default axis lines
    axis.ticks = element_line(color = "black", size = 0.5), # Customize tick marks
    axis.ticks.length = unit(-0.2, "cm"), # Move tick marks inside the axis
    panel.grid.major = element_blank(), # Remove major grid lines
    panel.grid.minor = element_blank(), # Remove minor grid lines
    panel.border = element_rect(color = "black", fill = NA, size = 1) # Add border around axes
  ) +
  scale_y_continuous(
    breaks = seq(-18, -6, by = 6), # Define y-axis tick intervals
    labels = function(x) x / 10, # Adjust y-axis tick labels to a simpler scientific format
    expand = c(0, 0) # Remove default padding
  ) +
  scale_x_discrete(
    expand = expansion(mult = 0.1) # Add padding to the x-axis
  )

# Save the plot
ggsave(paste0(FigureFolder, "/Gonogo/bsdf_BIC_GNGd_prime.tiff"), width = 9, height = 7, units = "cm")
ggsave(paste0(FigureFolder, "/Gonogo/bsdf_BIC_GNGd_prime.pdf"), width = 9, height = 7, units = "cm")



```

```{r plot-save, echo=FALSE, message=FALSE, warning=FALSE}
model.GNGd_prime <- modelsum_GNGd_prime_bsdf[[which.min(performance_GNGd_prime_bsdf$BIC)]]
summary(model.GNGd_prime)
mu.formula <- as.character(model.GNGd_prime$mu.formula)[3]
sigma.formula <- as.character(model.GNGd_prime$sigma.formula)[2]
print(paste0("The best distribution of gamlss for ",str_split_i(as.character(model.GNGd_prime$mu.formula), "~", 1)[2], " is ", model.GNGd_prime$family[1], "; the best mu.df is ", substr(mu.formula, regexpr("\\)", mu.formula)-1, regexpr("\\)", mu.formula)-1), ", sigma.df is ", substr(sigma.formula, regexpr("\\)", sigma.formula)-1, regexpr("\\)", mu.formula)-1), "."))
print(paste0("Diagnosis.1, model of ", str_split_i(as.character(model.GNGd_prime$mu.formula), "~", 1)[2], " is converged."))

# residual plots & Q-Q plots
newpar <- par(mfrow = c(2, 2), mar = par("mar") + c(0, 1, 0,0),
              col.axis = "black", col = "blue4", col.main = "black",
              col.lab = "black", pch = 1, cex = 0.45, cex.lab = 1.2,
              cex.axis = 1, cex.main = 1.2)
plot(model.GNGd_prime, par=newpar)
# Detrended transformed Owen’s plots
dtop(model.GNGd_prime)
# residual plots & Q-Q plots
tiff(paste0(FigureFolder, "/Gonogo/diagnosis_mod_", str_split_i(as.character(model.GNGd_prime$mu.formula), "~", 1)[2], ".tiff"),res=600, width=4000, height=3000)
newpar <- par(mfrow = c(2, 2), mar = par("mar") + c(0, 1, 0,0),
              col.axis = "black", col = "black", col.main = "black",
              col.lab = "black", pch = 1, cex = 0.45, cex.lab = 1.2,
              cex.axis = 1, cex.main = 1.2)
plot(model.GNGd_prime, par=newpar)
dev.off()
# Detrended transformed Owen’s plots
tiff(paste0(FigureFolder, "/Gonogo/diagnosis_owenplot_mod_", str_split_i(as.character(model.GNGd_prime$mu.formula), "~", 1)[2], ".tiff"),res=600, width=4000, height=3000)
dtop(model.GNGd_prime)
dev.off()

```


### 2. Model sensitivity analyses (bootstrap)

To determine reliability and stability of our GAMLSS fitted trajectories, and to obtain confidence intervals on all parameter estimates obtained from the GAMLSS fitting procedure as described above, we ran 1,000 bootstrap iterations with stratified sampling with replacement. The bootstrap replicates were stratified by Sex, which maintains the relative proportions of the original datasets.

```{r S3_2_mod_sensitivity}
# 1. GNG d_prime
bootstrapdir <- paste0(interfileFolder, "/bootstrap/GNGd_prime")
centile_female_boot <- list()
centile_male_boot <- list()
centile_boot <- list()
for (i in 1:1000) {
  centile.tmp <- readRDS(paste0(bootstrapdir, "/centile_bootstrap_", i, ".rds"))
  if (centile.tmp$converged==T){
    centile_female_boot[[i]] <- centile.tmp$Centiles_female
    centile_male_boot[[i]] <- centile.tmp$Centiles_male
    centile_boot[[i]] <- (centile.tmp$Centiles_female+centile.tmp$Centiles_male) / 2
  }else{
    centile_female_boot[[i]] <- NA
    centile_male_boot[[i]] <- NA
    centile_boot[[i]] <- NA
  }
}
print(paste0(length(which(is.na(centile_female_boot))), " iterations are not converged."))
# remove NA elements
centile_female_boot <- centile_female_boot[!is.na(centile_female_boot)]
centile_male_boot <- centile_male_boot[!is.na(centile_male_boot)]
centile_boot <- centile_boot[!is.na(centile_boot)]

centile_female_boot_3d <- array(unlist(centile_female_boot), dim = c(9, ncol(centile.tmp$Centiles_female), length(centile_female_boot)))
centile_male_boot_3d <- array(unlist(centile_male_boot), dim = c(9, ncol(centile.tmp$Centiles_male), length(centile_male_boot)))
centile_boot_3d <- array(unlist(centile_boot), dim = c(9, ncol(centile.tmp$Centiles_female), length(centile_boot)))

quantile.median <- data.frame(matrix(NA, ncol(centile.tmp$Centiles_female), 9*3))
names(quantile.median) <- c(paste0("female_", rownames(centile.tmp$Centiles_female)), paste0("male_", rownames(centile.tmp$Centiles_female)), paste0("all_", rownames(centile.tmp$Centiles_female)))
quantile.P2.5 <- data.frame(matrix(NA, ncol(centile.tmp$Centiles_female), 9*3))
names(quantile.P2.5) <- c(paste0("female_", rownames(centile.tmp$Centiles_female)), paste0("male_", rownames(centile.tmp$Centiles_female)), paste0("all_", rownames(centile.tmp$Centiles_female)))
quantile.P97.5 <- data.frame(matrix(NA, ncol(centile.tmp$Centiles_female), 9*3))
names(quantile.P97.5) <- c(paste0("female_", rownames(centile.tmp$Centiles_female)), paste0("male_", rownames(centile.tmp$Centiles_female)), paste0("all_", rownames(centile.tmp$Centiles_female)))

for (i in 1:9) {
  # female
  ## median
  quantile_female.vec <- centile_female_boot_3d[i, , ]
  quantile_female.median <- lapply(1:dim(quantile_female.vec)[1], function(x) median(quantile_female.vec[x,]))
  quantile_female.median <- unlist(quantile_female.median)
  quantile.median[,i] <- quantile_female.median
  ## P2.5
  quantile_female.P2.5 <- lapply(1:dim(quantile_female.vec)[1], function(x) quantile(quantile_female.vec[x,], probs=0.025))
  quantile_female.P2.5 <- unlist(quantile_female.P2.5)
  quantile.P2.5[,i] <- quantile_female.P2.5
  ## P97.5
  quantile_female.P97.5 <- lapply(1:dim(quantile_female.vec)[1], function(x) quantile(quantile_female.vec[x,], probs=0.975))
  quantile_female.P97.5 <- unlist(quantile_female.P97.5)
  quantile.P97.5[,i] <- quantile_female.P97.5
  
  # male
  ## median
  quantile_male.vec <- centile_male_boot_3d[i, , ]
  quantile_male.median <- lapply(1:dim(quantile_male.vec)[1], function(x) median(quantile_male.vec[x,]))
  quantile_male.median <- unlist(quantile_male.median)
  quantile.median[,i+9] <- quantile_male.median
  ## P2.5
  quantile_male.P2.5 <- lapply(1:dim(quantile_male.vec)[1], function(x) quantile(quantile_male.vec[x,], probs=0.025))
  quantile_male.P2.5 <- unlist(quantile_male.P2.5)
  quantile.P2.5[,i+9] <- quantile_male.P2.5
  ## P97.5
  quantile_male.P97.5 <- lapply(1:dim(quantile_male.vec)[1], function(x) quantile(quantile_male.vec[x,], probs=0.975))
  quantile_male.P97.5 <- unlist(quantile_male.P97.5)
  quantile.P97.5[,i+9] <- quantile_male.P97.5
  
  # all
  ## median
  quantile.vec <- centile_boot_3d[i, , ]
  quantile_all.median <- lapply(1:dim(quantile.vec)[1], function(x) median(quantile.vec[x,]))
  quantile_all.median <- unlist(quantile_all.median)
  quantile.median[,i+18] <- quantile_all.median
  ## P2.5
  quantile_all.P2.5 <- lapply(1:dim(quantile.vec)[1], function(x) quantile(quantile.vec[x,], probs=0.025))
  quantile_all.P2.5 <- unlist(quantile_all.P2.5)
  quantile.P2.5[,i+18] <- quantile_all.P2.5
  ## P97.5
  quantile_all.P97.5 <- lapply(1:dim(quantile.vec)[1], function(x) quantile(quantile.vec[x,], probs=0.975))
  quantile_all.P97.5 <- unlist(quantile_all.P97.5)
  quantile.P97.5[,i+18] <- quantile_all.P97.5
  
}

n_points <- nrow(quantile.median)
quantile.median$age <- seq(min(GNG_data$Age_year), max(GNG_data$Age_year), length.out = n_points)
quantile.P2.5$age <- seq(min(GNG_data$Age_year), max(GNG_data$Age_year), length.out = n_points)
quantile.P97.5$age <- seq(min(GNG_data$Age_year), max(GNG_data$Age_year), length.out = n_points)

# plot
ggplot()+
  geom_jitter(data = GNG_data, aes(x = Age_year, y = d_prime), color = "grey", alpha = 0.3, width = 0, height = 0.1) +
  geom_line(data=quantile.median, aes(x=age, y=all_quantiles0.5), linetype="solid", linewidth=0.5)+
  geom_line(data=quantile.P2.5, aes(x=age, y=all_quantiles0.5), linetype=2, linewidth = 0.25, color = "red")+
  geom_line(data=quantile.P97.5, aes(x=age, y=all_quantiles0.5), linetype=2, linewidth = 0.25, color = "red")+
  labs(x="Age(years)", y="d'", title="Bootstrap 95% CI of Go/No-go")+
  theme_classic()+
  scale_x_continuous(name="Age(years)", limits = c(11, 18),breaks = seq(11, 18, by = 1))+
  theme(plot.title = element_text(size=8.5, hjust=0.5, color = "black"),
        axis.text = element_text(size=8.5), axis.title = element_text(size=8.5), color = "black")
ggsave(paste0(FigureFolder, "/Gonogo/bootstrap_P50_95CI_GNGd_prime_all.tiff"), width=9, height=7, units = "cm")
ggsave(paste0(FigureFolder, "/Gonogo/bootstrap_P50_95CI_GNGd_prime_all.pdf"), width=9, height=7, units = "cm")
# # plot female-male
# ggplot()+
#   geom_point(data=GNG_data, aes(x=Age_year, y=d_prime), color="grey", alpha=0.5)+
#   geom_line(data=quantile.median, aes(x=age, y=female_quantiles0.5), linetype="solid", linewidth=0.5, color="red4")+
#   geom_line(data=quantile.P2.5, aes(x=age, y=female_quantiles0.5), linetype=2, linewidth=0.25, color="red")+
#   geom_line(data=quantile.P97.5, aes(x=age, y=female_quantiles0.5), linetype=2, linewidth=0.25, color="red")+
#   geom_line(data=quantile.median, aes(x=age, y=male_quantiles0.5), linetype="solid", linewidth=0.5, color="blue4")+
#   geom_line(data=quantile.P2.5, aes(x=age, y=male_quantiles0.5), linetype=2, linewidth=0.25, color="blue")+
#   geom_line(data=quantile.P97.5, aes(x=age, y=male_quantiles0.5), linetype=2, linewidth=0.25, color="blue")+
#   labs(x="Age (years)", y="d'", title="Bootstrap 95% CI of Go/No-go")+
#   theme_classic()+
#   theme(plot.title = element_text(size=20, hjust=0.5),
#         axis.text = element_text(size=20), axis.title = element_text(size=20))
# ggsave(paste0(FigureFolder, "/Gonogo/bootstrap_P50_95CI_GNGd_prime_bySex.tiff"), width=16, height=14, units = "cm")

```
## 4 Plot normative centiles

```{r plot_normative_trajectories}
# # 1) GNG
# ## set quantiles
# quantiles<-c(0.01, 0.025, 0.05, 0.25, 0.5, 0.75, 0.95, 0.975, 0.99)
# n_quantiles <- length(quantiles)
# n_points <- nrow(GNG_data)
# Centiles_male <- array(NA, dim = c(n_quantiles, n_points))
# Centiles_female <- array(NA, dim = c(n_quantiles, n_points))
# x_female <- seq(min(GNG_data$Age_year), max(GNG_data$Age_year), length.out = n_points)
# x_male <- seq(min(GNG_data$Age_year), max(GNG_data$Age_year), length.out = n_points)
# gam.data2 <- GNG_data %>% select(c("d_prime", "Age_year", "Sex", "ID")) %>% drop_na()
# gam.data2$Age_year <- gam.data2$Age_year
# gam.data2$Sex <- as.factor(gam.data2$Sex)
# 
# for (i in 1:n_quantiles){
#   command <- "Qua <- getQuantile(model.GNGd_prime, quantile=quantiles[i], term = 'Age_year', fixed.at = list(Sex='F'), n.points = n_points)"
#   eval(parse(text=command))
#   Centiles_female[i,] <- Qua(x_female)
#   
#   command <- "Qua <- getQuantile(model.GNGd_prime, quantile=quantiles[i], term = 'Age_year', fixed.at = list(Sex='M'), n.points = n_points)"
#   eval(parse(text=command))
#   Centiles_male[i,] <- Qua(x_male)
# }
# 
# Centiles <- (Centiles_female + Centiles_male) /2
# Term_conrti <- predict(model.GNGd_prime, what="mu", newdata = gam.data2, type="term")
# Age_Term <- gam.data2$d_prime - Term_conrti[,2]
# X  <- x_female
# ggplot()+
#   #geom_point(data=gam.data2, aes(x=Age_year, y=Age_Term), color="grey", alpha=0.3)+
#   geom_line(aes(x=X, y=Centiles[1,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[2,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[3,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[4,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[5,]), linetype="solid")+
#   geom_line(aes(x=X, y=Centiles[6,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[7,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[8,]), linetype="dashed")+
#   geom_line(aes(x=X, y=Centiles[9,]), linetype="dashed")+
#   scale_y_continuous(name="d'", sec.axis = sec_axis(~ . , name = "Centile", breaks = c(Centiles[1,n_points], Centiles[2,n_points],Centiles[3,n_points],Centiles[4,n_points], Centiles[5,n_points], Centiles[6,n_points], Centiles[7,n_points]), labels=c("1%","2.5%", "5%", "25%", "50%", "75%", "95%", "97.5%", "99%")))+
#   labs(x="Age (years)", title="Developmental trajectory of Go/No-go d'")+
#   theme_minimal()+
#   theme(plot.title = element_text(size=8.5, hjust=0.5),
#         axis.text = element_text(size=8.5), axis.title = element_text(size=8.5),
#         panel.border = element_rect(color="black", fill=NA, size=1))
# 
# ggsave(paste0(FigureFolder, "/Gonogo/normative_trajectories_GNGd_prime.tiff"), width=16, height=14, units="cm")
# 
# ## computed the centile
# mu_pred <- predict(model.GNGd_prime, newdata = gam.data2, what = "mu", type = "response")
# sigma_pred <- predict(model.GNGd_prime, newdata = gam.data2, what = "sigma", type = "response")
# nu_pred <- predict(model.GNGd_prime, newdata = gam.data2, what = "nu", type = "response")
# tau_pred <- predict(model.GNGd_prime, newdata = gam.data2, what = "tau", type = "response")
# observation <- gam.data2$d_prime
# centile <- pSEP1(observation, mu = mu_pred, sigma = sigma_pred, nu = nu_pred, tau = tau_pred)
# gam.data2$centile_GNGd_prime <- centile
# summary(gam.data2$centile_GNGd_prime)
# plot(density(gam.data2$centile_GNGd_prime), main = "Density Plot of Data", xlab = "Value", col = "blue")
# 
# write.csv(gam.data2, paste0(interfileFolder, "/GNG_data_centile.csv"), row.names = F)




```
